\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[margin=0.5in]{geometry}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{calc}
\newtheorem{question}{Question}
\newtheorem*{question*}{Question}
\newtheorem{theorem}{Theorem}
\newtheorem*{theorem*}{Theorem}
\newtheorem{lemma}{Lemma}

\theoremstyle{definition}
\newtheorem{answer}{Answer}
\newtheorem*{answer*}{Answer}


\title{Complex Analysis Homework 8}
\author{Colin Williams}

\begin{document}
\maketitle

\section*{Question 3}
Let $f$ be a holomorphic function in $\mathbb{C}$ such that $f(z) \to 0$ as $|z| \to \infty$. Prove that $f$ is identically zero.

\begin{proof}{$ $}
\\Since $f$ is entire, we know we can express $f$ as a power series centered at some $z_0 \in \mathbb{C}$. For convenience, choose $z_0 = 0$. Thus, 
\[f(z) = \sum_{n = 0}^{\infty} a_nz^n \quad \text{for all $z \in \mathbb{C}$.}\]
From here, assume that $f$ is not a constant function. This means that there exists some set $S = \{n: a_n \neq 0$ and $n \geq 1\}$ that is nonempty. Thus,
\begin{align*}
f(z) = \sum_{n = 0}^{\infty} a_nz^n = a_0 + \sum_{n \in S}a_nz^n
\end{align*}
Using this expression, I will take the limit as $|z| \to \infty$. Since the assumption on $f$'s limit at infinity must hold for all rays that extend to infinity I will choose to take $z$ along the path $\{z: $ Re$(z) > 0$ and Im$(z) = 0\}$, the positive real axis. Therefore for $z = x \in \mathbb{R}^+$,
\begin{align*}
\lim_{|z| \to \infty} f(z) = \lim_{x \to +\infty} f(x) &= \lim_{x \to +\infty}\left(a_0 + \sum_{n \in S}a_nx^n\right)\\
&= a_0 + \lim_{x \to +\infty}\sum_{n \in S}a_nx^n
\end{align*}
Note that due to the way $S$ was defined, all of the coefficients $a_n$ in the limit term must be nonzero. This means that as $x \to \infty$, this limit also goes to $\infty$ (in modulus, since the coefficients may be complex). However, this contradicts $f(z) \to 0$ as $|z| \to \infty$, so our assumption must have been wrong that $f$ is non-constant. This means that the set $S$ described above must actually be the empty set. Thus, in order for $f(z) \to 0$ as $|z| \to \infty$, we need to impose that $a_0$ is 0. However, at this point we have concluded that $a_n = 0$ for all $n \in \mathbb{N}_0$, which means $f$ is identically zero.
\end{proof}

\end{document}